\subsection{External Interface Requirements}
\subsubsection{User Interfaces}
\subsubsection{Hardware Interfaces}
\subsubsection{Software Interfaces}
\subsubsection{Communication Interfaces}


\subsection{Functional  Requirements}
  \G{1} Allow users to notify authorities about traffic violations.
  \R{1} 
  \G{2} Allow users to send pictures of violations.
  \R{2} Images should be clear so that the license plate can be readen easily.
  \R{3} The type of violation should be clear in the picture.
  \G{3} Be sure every information uploaded is never altered
  \G{4} Automatically add metadata to the reported pictures
  \G{5} allow users to mine information recorded
  \G6} have at least two different  priviledge for mining data
  \G{7} generate traffic tickets
  \G{8} Autorities can see the the licence plates of violators, regular users cannot

think about use cases @both

\subsubsection{Use Cases}
This section contains all the use cases initially described with the use cases UML model, then the most important Use Case have their own table which provide further details such as: involved actors, entry conditions, ﬂow of events, exit conditions and exceptional conditions.

\subsubsubsection{User Page use cases}
 
 \subsubsubsection{Reporting Violation use cases}

\subsubsection{User}
\subsubsection{Third party}

\subsubsection{Requirements}
Requirements in order to satisfy the goals
\begin{enumerate}
  \requirement{1} test
\end{enumerate}



%remember to chech if the licence plate exists or not!!!!
\subsection{Performance Requirements}


\subsection{Design Constraints}%%%%%%%%%%%%%%%%%%%T.

\subsubsection{Standards compliance}
The app shoudld be available for the two main operating systems of smartphones: Android Os and Apple iOS.\\
The traffic violations which can be reported should be compliant to the local traffic code where the app will be used.\\
For an use in Italy the app should be compliant to the "Codice della Strada", in particular parking violations are reported in Art. 157.\\


\subsubsection{Hardware limitations}
The app will have a server side and a client side (smartphone).
On server side limitations can be the size of available storage and the bandwidth.
On smartphone side we have the network connectivity (3G/4G connection) and GPS limitations in some areas.

\subsubsection{Any other constraint}
Application should be compliant to European GDPR and don't track users.

\subsection{Software System Attributes} %%%%%%%%%%%%%@S.
\subsubsection{Simple User Interface}
The user interface has to be as simple and intuitive as possible, the application should allow an average user to set up an account and start using the application understanding its functionality in no more than a dozen minutes. In addition there should be a complete tutorial to makes it easy using the application. 

\subsubsection{Reliability}
The application provides a reliable service in which individual users can easily log in and report the violations in the most optimal way. Furthermore it Warranties that the chain of custody of the information coming from the users is never broken, and the information is never altered. This would provide a secure and reliable system. In addition, if the license plate	is not readable from the picture the application should warn the user to send an other photo.
\subsubsection{Availability}
The application must offer the maximum availability, granting its service every day at any time (24/7). The lack of service must be minimal.Reporting violation and taking the information about the vioalation coming from SafeStreets must be active every day at any time. The lack of service is acceptable only if it is due to maintenance. In this case, users must receive a warning 48 hours before.
\subsubsection{Security}
The application need to be safe and it does not have particular security concerns except the ones related to unauthorized login. The login of Users and especially of authorities must be very safe to avoid reporting. Moreover, the means of communication must be encrypted to save the confidentiality of information sent to SafeStreets.
\subsubsection{Maintainability}
The application will be maintained and designed in such a way it makes it easier to maintain and it shoul be understandable for both the users and the authorities. Furthermore, the system will put eﬀort in keeping the live data services (such as highlighting the streets with the highest frequency of violations or the vehicles that commit the most violation) always online.
\subsubsection{Portability}
Portability of user data from a device to another is possible by entering personal login data. Also the application will be able to run for devices with different operating systems. Trackme wants to focus on the both Android iOS market and Apple iOS , because Android is the largest OS in the world and it is expected that the market share of Apple iOS will increase in the coming years.
